Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2020-01-31 write_up/reviewer_response_seperate.tex

\documentclass[10pt]{letter}

\usepackage[margin=2.54cm, a4paper]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage{xcolor}
%%\usepackage[final]{changes}
\begin{document}

\underline{Editor's comments} \\
\\
\textit{
After considering the comments of the two reviewers, which are provided below,
I think your manuscript should be acceptable for publication after satisfactory
revision.  Please address the reviewers' comments when revising your
manuscript. Thank you again for submitting your manuscript to Ecological
Modelling.
}

Thank you for your comments, we have provided a detailed response to each of
the points made by the reviewers along with a track-changed (as well as a
`clean') revision of the manuscript. In addition, we provide a short vignette
detailing an example application and R code for the framework, which we hope
will widen accessibility and take up of the modelling framework. We hope that
together this satisfies your requirements and look forward to seeing the
manuscript published. \\

@@

\underline{Reviewer 1 comments} \\

\textit{This paper introduces a simulation framework for assessing the effects
	of different spatial and temporal observation scales on management of
	mixed fisheries. An application of the framework is presented, and the
	findings from the example application provided insights into the
	importance of data resolution on design and effectiveness of closed
	areas. The model code is included as an R package so that other
	researchers will be able to implement it readily to address a wide
	variety of management questions. The question of appropriate scales is
	an important one, and I think this will be a valuable tool for
	researchers and managers. I recommend that it be published after minor
	revisions.}

Thank you, we are grateful for your comments that have improved our manuscript
and look forward to our work reaching and being used by a broad audience.

	\begin{center}
	\begin{longtable}{p{8cm} | p{8cm}}
%	\caption{Highly resolved spatiotemporal simulations for exploring mixed
%	fishery dynamics}
		\toprule
		Comment & Response \\
		\\
		\hline
		\\
\textbf{Asbstract} & \\
\\
I think it would be helpful to mention the name of the R package (MixFishSim)
that accompanies this paper somewhere in the abstract. People will search for
the package name, it would be nice if the term was included in the abstract so
the paper will show up in the search too. & We have included
\textit{MixFishSim} in the first sentence of the abstract. \\
\\
``true underlying populations" - somehow make sure readers know this is
referring to simulated populations. & We have changed to "true (simulated)
underlying populations" on line 10 of the abstract. \\
\\
Could add something like "bycatch avoidance", or something like that, somewhere
in key words or abstract; people searching for that term would be glad to find
this paper, I would think! & Done, see keywords. \\ 
\\
I think the abstract could be streamlined a bit. You seem to have 2 major
objectives with this paper: 1) introducing and describing the simulation
framework that could answer a number of important management questions, and 2)
demonstrating its usefulness with an example application. One full paragraph
for each should be adequate, with a conclusion that states the usefulness of
the framework for answering a number of fisheries management questions.  &
We've worked to shorten and strengthen the abstract as suggested. \\
\\
\hline
\\
\textbf{Introduction} &  \\
\\
Line 62: ``Do different sources of sampling-derived fisheries data reflect"… &
Corrected at line 73. \\
\\

@@

Why was the Matern covariance structure chosen? I am just curious about this;
does it reflect the spatial autocorrelation of animal distributions better than
a Gaussian or other type of covariance structure? & We used the Matérn
covariance structure as it is flexible, and contains the exponential form as a
special case.  We've added text at line 170 to say ``We use the most commonly

@@

non-linearly...." \\ 
\\
It would be helpful to have explanation of thermal tolerance earlier than line
155 & We have now added a sentence at the beginning of the section (lines 153 -
154) that reads ``described by a set of probabilities.  Stochastic
probabilities are affected by the suitability of habitat, temperature in a cell
and the thermal tolerance of a population to that temperature." \\

@@

section. \\
\\
Line 187, make tenses consistent (e.g. determined vs. determines) - also this
sentence is a little awkward to read. & We have changed lines 208 - 218
so that it reads in the past tense and rewritten the paragraph to improve
readability. \\

@@

\\
\textbf{Results} &  \\
\\
Line 376: What does ``Visualized using Gerritsen (2014)" mean? & We've now
added to the caption of Current Figure 3: ``The figure shows catch composition
at each spatial unit represented by a square pie chart of the four populations.
The area of each colour is proportional to the weight of each population caught
in that unit. Figure produced with the R package `mapplots' (Gerritsen et al
2014)." \\ 

@@

\\
Line 397: Are these the same figures in Table 7? If so, just refer to the table
and summarize & Yes, they are the same and we agree this change improves
readability and the two final paragraphs in section 4.2 (lines 424 - 432) have
been revised accordingly. \\ 

@@

\\
Line 400: move \% sign & This paragraph has been revised so the point
	is redundant. \\

@@

\\
Line 406: ``(in red)" - leave reference to color for figure legend & Removed
reference to color on line 435. \\

@@

\\
Line 410: ``Again" doesn't need to be there, same in line 413 & Agree, it has
been removed on line 430. \\

@@

\\
Line 416: This section is a little confusing and needs to be
refined/streamlined. & We have now revised this section to clarify and improve
readability. For example, shortening sentences and ensuring one point is made
per sentence (lines 443 - 455). \\

@@

Line 418: This paragraph should be in methods. But you did it for all
populations, right? Not just population 3? & That's correct, the closures
affected all populations but the closures were targeted to reduce fishing
mortality on population 3. We have clarified and moved to the methods section
now at lines 378 - 386.

@@

\textbf{Discussion / Conclusion} &  \\
\\
The discussion and conclusion overlap a bit; I felt I was reading similar
things over again; perhaps these can be streamlined? & We have reviewed but
believe each paragraph makes an independent point except the final paragraph,
which does repeat some of the previous conclusions. As such, we have removed
the final paragraph of the conclusions. \\

@@

\\
Line 560: change ``reduced" to ``reduce" & Done on line 581. \\

@@

\\
Line 663: change ``hypothesis" to ``hypotheses" & This paragraph has now been
removed at the suggestion of reviewer 2. \\

@@

\textbf{Figures} &  \\
\\
Figure 1: nicely summarizes the model. It took me a little bit to figure out
that ``Rec" referred to recruitment - even though it was in the legend (I
missed it when I read it the first time)… is it possible to choose an
abbreviation that makes it more obvious, maybe something like ``Recruit" or
even ``Recr"? It also occurs to me that there is an opportunity to introduce
the terminology from your R package here to make it very clear to the people
using your code how the functions work together… this is only an idea though…
or maybe a similar figure could be included with the vignette. & We have
changed to `Recr' to make clearer. Rather than change the schematic, we have
included a short example vignette demonstrating the use of the code to increase
accessibility and further uptake. \\

@@

\underline{Reviewer 2 comments} \\

\textit{The paper Dolder et al. presents a new highly resolved spatiotemporal
	model that simulates populations of species and fishery dynamics to
	assess if data from commercial catches and fixed-site sampling surveys
	on different spatiotemporal scales represent the real distribution of
	the populations, and if these data are effective to base  management
	programs. Moreover, they presents other applications of the model.} \\

\textit{This is a very interesting paper, and the model provides several
	applications for management programs. I have only few greater questions
	and some small issues, most of them about the presentation of the
	information.}  \\

We thank the reviewer for their comments and suggestions that have greatly
improved the presentation and interpretation of our methods and results.

@@

\begin{center}

	\begin{longtable}{p{8cm} | p{8cm}}
%	\caption{Highly resolved spatiotemporal simulations for exploring mixed
%	fishery dynamics}
		\toprule
		Comment & Response \\
\\
\hline
\\	
	\textbf{General comments} &  \\
\\
		 How many species does the model simulate? The authors refer to
		 the issue of catching unwanted species (vulnerable or low
		 quota species) when available quota species is caught, and it
		 suggested me that populations of different species is modelled
		 at the same time. However, they  did not describe how many
		 species could be simulated in each simulation, only that four
		 populations were simulated. Does the populations simulated in
		 different simulations, or all of them are simulated
		 simultaneously? The results indicate that the four populations
		 were simulated in the same simulation. Please, clarify this in
		 the MM.  & We now emphasise on line 100 that the framework
		 allows the user to define as many species as required. There
		 will be some computational/memory cap but we see no reasons
		 why you could not include 10s or more. We chose four to keep
		 the analysis more tractable. All the populations are part of
		 the same system, irrespective of the number of species
		 included, hence they are simulated in the same simulation.\\
\\
There are too many figures and they should be better edited. Why the name of
the row and columns are inside the graphics? The axes scales and the axes title
should be greater. I would also send the figure 2, 3 and 9 as supplementary
data.  & We have revised the main figures to increase text size and changed to
bold font; we have also moved figures 2 and 3 to the supplementary figures. We
have retained figure 9 (Current Figure 7) as we believe it gives understanding
to the fishery - population interactions before and after the spatial closures
which is important for the narrative of the example application. \\
\\
The legends of the supplementary figures should be more informative. In the
Figure S2, what the light gray spots are? Habitat preference? Are the squares
the spawning areas? In the figure S3, are each square a week?  & We have
revised the captions for the supplementary figures to provide additional
information, including the issues you've identified. Specifically, Figure S2
(Current Figure S3): ``with the darker colour showing greater habitat
suitability". Figure S3 (Current Figure S7): the caption reads ``for 52 separate
weeks"

\\
I am not native English, but the language seems good for me. However, I missed
several commas along the text that make the sentences too long and hard to
understand. I suggest a revision of this.  & We have revised the text to ensure
readability. \\

\hline
\\
\textbf{Small issues} &  \\
\\
Line 14 - 18: This phrase is too long and hard to understand. Please, rephrase
this in shorter sentences to clarify this idea. & These sentences have been
revised to clarify in lines 14 - 21.  \\
\\
Lines 20 - 43: These two paragraphs seem redundant. & We believe these
paragraphs set the context for an important premise of the paper: That
identifying the correct spatial scale for management is important to achieve
the anticipated outcomes; particularly in mixed fisheries where there is a
`cost' through loss of fishing opportunities for other fisheries which
management seeks to minimise. However, we have revised at lines 23 - 34 to make
our point clearer to the reader. \\
\\
Line 68 - 72: The authors mentioned that the MixFishSim could be used to infer
if fisheries data are the real community structure. I suggest adding one or two
phrases to explain how the model could help in this. & We explain that as our
community structure is simulated and therefore known, by comparing our inferred
community structure from commercial catches with our known true structure we
can understand how biases introduced by using commercial fishing as a sample
affects our understanding. These points are covered on lines 79 - 83.\\
\\
Line 90. The authors presented the time-step of each module, except the
Recruitment dynamics. The recruitment dynamics probably follow the population
dynamic, but it would be interesting present this explicitly. & Recruitment
occurs along with other population dynamics, but only during defined periods
for each population. We've clarified by saying in lines 100 - 102 ``Population
dynamics for any number of species, as chosen by the user, operate on a daily
time-step \textit{(with recruitment occurring only during defined seasons for
	each population),} while.."
\\
\\
Line 282: How these population parameters were selected? Randomly? Using real
data? Or the authors only created them? & The demographic parameters were
chosen by the authors to broadly reflect population dynamics for a four-species
assemblage representing species typically found in a demersal fishery. We have
clarified by including in lines 310 - 313 the sentence: ``The population
demographics were chosen to broadly represent three mobile low-medium value
groundfish species and one high value species with low mobility, with the
dynamics hypothetical but as you might expect to find in a typical demersal
fishery." \\
\\ 
Line 426: What does adapted means in this context? Exploring new opened areas?
& Yes, we have clarified in the text on lines 446 - 447 that the
fisheries ``adapted" to the closures textit{by fishing new areas of high
	abundance to fish}\\
\\
Line 613: Do not use parenthesis inside of other parenthesis. & We have changed
on lines 632 from ``( e.g." to ``, e.g." to eliminate one set of parentheses.
\\
\\
Table 2 and table 3 are not cited in the text Citation of the supplementary
figures are out of order & This is now corrected with references inserted for
Table 2 (line 204) and Table 3 (line 274) and the supplementary figures
reordered. \\
\\
Figure 3: Individual years ARE the light grey lines    & Corrected. \\
\\
Figure 4. What do the purple spots represent? Describe these spots in the
capture & This has been clarified (in Current Figure 2) to be the revenue at
each location (darker areas indicate higher revenue). \\ 
\\
Figure 7. Add what ``res"  means in the caption.  & Have clarified in the
legend text that it means ``resolution" \\
\\
Figure 8. What F means? & Changed to read ``Fishing mortality" \\
\\
		\bottomrule
	\end{longtable}

### 2020-01-31 write_up/mixfishsim_ecolmod_revisions_clean.tex
Revised manuscript

\documentclass[review]{elsarticle}

@@

\usepackage[final]{changes}

@@

%% Harvard
\bibliographystyle{model2-names.bst}\biboptions{authoryear}
%%%%%%%%%%%%%%%%%%%%%%%
%% correct equation line numbering

@@

\author[1]{Cóilín Minto}
\author[3]{Jean-Marc Guarini}
\author[4,5]{Jan Jaap Poos}

@@

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model \emph{MixFishSim} incorporating: i) delay-difference
population dynamics, ii) population movement using Gaussian Random Fields to
simulate patchy, heterogeneously distributed \added{and moving fish}
populations, and iii) fishery dynamics for multiple fleet characteristics based
on population targeting under an explore-exploit strategy.\deleted{ This is
	implemented via a mix of correlated random walk movement (for
	exploration) and learned behaviour (for exploitation) phases of the
	fisheries. }\\ 
%%
\deleted{Fifty years of sub-daily fishing activity was simulated and used to
	draw inference on the underlying community structures. W}\added{We
	applied \emph{MixFishSim} to\deleted{draw}}\deleted{compared}
infer\deleted{ence}\deleted{s} \added{\deleted{on}community structure}
\added{when using data generated from:} \deleted{based on}commercial catch,
a\deleted{simulated} fixed-site sampling survey design and the true
\added{(simulated)} underlying populations.  \deleted{W}\deleted{\added{In
		doing so w}}\added{W}e \added{thereby} \deleted{i)}establish
the potential limitations of fishery-dependent data in providing a robust
\replaced{characterisation}{picture} of spatiotemporal distributions.\deleted{;
	and then ii) simulated an area closure based on areas defined from the
	different data sources at a range of temporal and spatial
	resolutions.}\deleted{Our framework allows users to explore the
	assumptions in modelling observational data and evaluate the underlying
	dynamics of such approaches at a fine spatial and temporal scale. In
	application to a mixed fishery exploiting four different populations w}
\deleted{\added{W}e found d}\added{D}ifferent spatial patterns were evident and
\deleted{that }the effectiveness of the spatial closure reduced when data were
aggregated across larger spatial areas. \deleted{; and then
	ii)}\deleted{\added{We then simulated an area closure based on areas
		defined from the different data sources at a range of temporal
		and spatial resolutions.}} \added{A simulated area
	closure showed that} \replaced{a}{A}ggregation across time periods has
less of a negative impact on the closure success than \added{aggregation} over
space. \deleted{ and w}\added{W}hile not as effective as when based on on the
true population, closures based on high catch rates observed in commercial data
were still able to reduce fishing on a protected species. \\

\added{Our framework allows users to explore the assumptions in modelling
	observational data and evaluate the underlying dynamics of such
	approaches at a fine spatial and temporal resolutions. From our
	application w}\deleted{W}e conclude that commercial data, while
containing bias, provide a useful tool for managing catches in mixed fisheries
if applied at the correct spatiotemporal scale. \\
%%
\end{abstract}

@@

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time with varying knowledge of species distributions.
As fishers do not have full control over what species they select when fishing
in `mixed fisheries' it can result in catch of low quota or protected species.
If over-quota catch of a species for which they have no quota is discarded
without being accounted for it limits our ability to control fishing mortality
\citep{Alverson1994, Crowder1998, Rijnsdorp2007} and the ability to manage
fisheries for the biological and economic sustainability \citep{Ulrich2011a,
	Batsleer2015}.\\

There is increasing interest in technical solutions such as gear and spatial
closures as measures to reduce unwanted catch\added{ which is often discarded}
\citep{Kennelly2002, Catchpole2008, Bellido2011, Cosgrove2019}\added{.
	A}\deleted{ and a}daptive spatial management strategies have been
proposed as a way of reducing over-quota discards \citep{Holmes2011,
	Little2014, Dunn2014a}. However, if fisheries are to reduce unwanted
catch through spatial avoidance, an in-depth understanding of spatiotemporal
fishery dynamics is required. \\

Understanding the correct scale for spatial management measures to be effective
is crucial as it enables implementation of effective solutions which minimise
economic impact \citep{Dunn2016}. For example, the problem can be to identify a
scale that promotes species avoidance for vulnerable or low quota species while
allowing continuance of sustainable fisheries for available quota species.
Identifying the correct spatial scale remains a challenge because data on fish
location at high temporal and spatial resolutions is expensive and difficult to
collect and proxies are usually inferred from scientific surveys or commercial
catches with limited spatial and temporal resolution. Thus, implementation of
spatial measures is hampered by a lack of knowledge of fish and fishery
spatiotemporal dynamics and understanding of the scale at which these processes
become important for management. \\ \\

Identifying appropriate spatial scales for fisheries closures \deleted{has been a
highlighted a}\added{i}s crucial to their success \citep{Costello2010, Dunn2016}.
Inference on fisheries spatial dynamics is hampered where spatial information
is coarse due to low resolution reporting of fisheries catch which is
aggregated across larger gridded areas \citep{Branch2005}. Further, if data
does not allow identification of spatial features it may lead to poorly sited
closures \replaced{that}{which} are ineffectual or have unintended consequences. For example,
increased benthic impact on previously unexploited areas from the cod closure
in the North Sea were observed without the intended effect of reducing cod
exploitation \citep{Rijnsdorp2001,Dinmore2003}).\\

More refined spatiotemporal information has since become available through the
combination of logbook and Vessel Monitoring System (VMS) data \citep{Lee2010,
	Bastardie2010, Gerritsen2012, Mateo2016} and more real-time spatial
management has been possible \citep[e.g.][]{Holmes2011}.  However, fishers
establish favoured fishing grounds through an explore-exploit strategy
\citep{Rijnsdorp2011, Bailey2018} where they search for areas with high catches
and then use experience to return to areas where they have experienced high catch
in the past. This leads to an inherently biased sampling where target species
are over-represented in the catch as fishers exploit areas of high abundance.
There is a need to understand the influence of these biases on any spatial
management measures which are implemented based on inference from commercial
landings or catch data. \\

@@

\begin{enumerate}
	\item Do different source\added{s} of sampling-derived fisheries data
		reflect\deleted{s} the underlying community structure? 	
	\item How do\deleted{es} data aggregation and data source impact on the success
		of spatial fisheries management measures?
\end{enumerate}

@@

A Discrete-event simulation (DES) model of a hypothetical fishery was developed
as a software package (\textit{MixFishSim}). The modular approach enabled
efficient computation by allowing for sub-modules implemented on time-scales
appropriate to capture \deleted{the }characteristic\added{s} of the different processes (Figure
1). \replaced{S}{The following s}ub-modules \deleted{were included }to capture the full system \added{comprised}: 1)
\replaced{p}{P}opulation dynamics, 2) \replaced{r}{R}ecruitment dynamics, 3) \replaced{p}{P}opulation movement, 4)
fishery dynamics.\\

Population dynamics \added{for any number of species, as chosen by the user,}
operate on a daily time-step \added{(with recruitment occurring only during
	defined seasons for each population)}, while population movement occurs
on a weekly time-step, with the fishing module operating on a tow-by-tow basis
(i.e.\added{,} multiple events a day). \\

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model \replaced{that}{which} models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals \citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (\replaced{see}{the full parameter list is detailed in } Table \ref{tab: pop_variable} \added{for all parameter details}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& \left(1 + \rho \right) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + W_{R-1} \cdot \left( \alpha_{d-1} \cdot
	R_{\tilde{y}\left(c\right)}\right) \right)
	\hspace{0.9cm} + \\
	& W_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y} \left(c\right)}
	\right) \\
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient\textcolor{blue}{(Check)}, shown to be equal
to $\mathrm{e}^{-K}$ when $K$ is the \deleted{growth }rate \added{at which the
	asymptote is approached} from a von Bertalanffy \deleted{logistic
}growth model \citep{Schnute1985}. $W_{R-1}$ is the average weight of fish
prior to recruitment, while $W_{R}$ is the average recruited weight.
$\alpha_{d}$ represents the proportion of fish recruited during that day for
the year, while $R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for
cell $c$. \\

@@

Recruitment is modelled as a function of adult biomass. In
\textit{MixFishSim}, it can either take the form of a stochastic Beverton-Holt
stock recruitment relationship, or a stochastic Ricker stock recruitment
relationship. The Beverton-Holt relationship is defined as\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha \deleted{\cdot} S_{c,d})}{(\beta + S_{c,d})} \\
	     \added{\ln(}R_{c,d}\added{)} \sim & \deleted{\log} N[(\replaced{\ln}{\log}(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes. The stochastic Ricker form \citep{Ricker1954} is:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
	\ln(R_{c,d}) \sim & N[(\ln(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the
density-dependent reduction in productivity as the SSB increases.

@@

Population movement is a combination of directed (advective) movement where at
certain times of year the population moves towards spawning grounds by
increasing the probabilities of moving into the spawning grounds from adjacent
cells, and random (diffusive) movement, governed by a stochastic process where
movement between adjacent cells is described by a set of probabilities.
\added{Stochastic probabilities are affected by the suitability of habitat,
	temperature in a cell and the thermal tolerance of a population to that
	temperature}.\\

\added{The combined process results in a population structure and movement
	pattern unique to each population, with population movement occurring
	on a weekly basis. \replaced{M}{The decision to m}odel\added{ing}
	population movement on a weekly timescale\deleted{ was to}
	reflect\added{s} that fish tend to aggregate in
	species\added{-}specific locations\deleted{ that have been} observed to
	last \replaced{between}{around } one \replaced{and}{to} two weeks
	\citep{Poos2007}. Therefore this process approximated the demographic
	shifts in fish populations throughout a year with seasonal spawning
	patterns }(Figure \ref{S-fig:5}).

>>>>

\documentclass[preprint]{elsarticle}

@@

%%\usepackage[final]{changes}

@@

%% Harvard
\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%%%%%%%%%%%%%%%%%%%%%%%
%% correct equation line numbering

@@

\author[1]{Cóilín Minto}
\ead{coilin.minto@gmit.ie}
\author[3]{Jean-Marc Guarini}
\ead{jean-marc.guarini@upmc.fr}
\author[4,5]{Jan Jaap Poos}
\ead{janjaap.poos@wur.nl}

@@

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model \emph{MixFishSim} incorporating: i) delay-difference
population dynamics, ii) population movement using Gaussian Random Fields to
simulate patchy, heterogeneously distributed and moving fish populations, and
iii) fishery dynamics for multiple fleet characteristics based on population
targeting under an explore-exploit strategy. \\

%%
We applied \emph{MixFishSim} to infer community structure when using data
generated from: commercial catch, a fixed-site sampling survey design and the
true (simulated) underlying populations. In doing so we thereby establish the
potential limitations of fishery-dependent data in providing a robust
characterisation of spatiotemporal distributions. Different spatial patterns
were evident and the effectiveness of the spatial closure reduced when data
were aggregated across larger spatial areas. A simulated area closure showed
that aggregation across time periods has less of a negative impact on the
closure success than aggregation over space. While not as effective as when
based on on the true population, closures based on high catch rates observed in
commercial data were still able to reduce fishing on a protected species. \\

Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal resolutions. From our application we conclude that
commercial data, while containing bias, provide a useful tool for managing
catches in mixed fisheries if applied at the correct spatiotemporal scale. \\
%%
\end{abstract}

@@

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time. Fishers generally only have partial knowledge of
species distributions and so limited control over what species they select when
fishing in `mixed fisheries'. This results in catches of vulnerable species and
species with low-quota. These species may be thrown overboard in a process
called discarding and discarding catches that are not recorded leads to biased
perception of the effects of fisheries on ecosystems. Ultimately the
unaccounted discards limit our ability to control fishing mortality
\citep{Alverson1994, Crowder1998, Rijnsdorp2007} and the ability to manage
biological and economic sustainability of fisheries \citep{Ulrich2011a,
	Batsleer2015}.\\

There is increasing interest in technical solutions such as gear adaptations
and spatial closures as measures to reduce discarding of unwanted catches
\citep{Kennelly2002, Catchpole2008, Bellido2011, Cosgrove2019}. Adaptive
spatial management strategies have been proposed as a way of reducing
over-quota discards \citep{Holmes2011, Little2014, Dunn2014a}. However, to
reduce unwanted catch through spatial measures requires an in-depth
understanding of the spatiotemporal dynamics of the fishery. \\

Effective spatial management requires implementation at appropriate spatial
scales. These spatial scales shape the trade-offs between protection of
populations and economic impacts on fisheries \citep{Dunn2016}. In mixed
fisheries, the problem is to identify a scale that promotes species avoidance
for vulnerable or low-quota species while allowing continuance of sustainable
fisheries for available quota species. Identifying the appropriate spatial
scale remains challenging because collecting data on fish distribution at high
temporal and spatial resolutions is expensive and difficult. Proxies for the
spatial distributions are usually inferred from fisheries-dependent data or
from fisheries-independent data. Fisheries-dependent data includes all data on
catch and effort from commercial fishing operations while fisheries-independent
data includes data collected on board scientific research vessels. \\

Inferences on fish distributions are hampered where spatial and temporal
information is coarse. Sampling designs for scientific research vessel surveys
generally aim for unbiased estimates of local abundance. However, high costs of
these surveys generally results in restrictions in terms the number of samples.
As a result, sampling is usually restricted to a few weeks a year, and sampling
stations are usually coarsely spaced. Moreover, the gear chosen for the survey
determines the selectivity for certain species and size classes within fish
communities. This selectivity determines the usefulness of relative occurrence
in survey catches as proxies for abundances in the fish communities. \\

Proxies for spatial distribution derived from commercial fisheries in theory
allow for much larger sample sizes. These commercial fisheries are often at sea
throughout the year, making may fishing hauls. However, spatial information
from fisheries is often limited because data on catch and effort is collected
or aggregated across larger gridded areas \citep{Branch2005}. If spatially
aggregated data does not allow identification of spatial features it may lead
to poorly designed spatial management measures that are ineffectual or have
unintended consequences \citep{Costello2010, Dunn2016}. For example, increased
benthic impact on previously unexploited  areas from the cod closure in the
North Sea were observed without the intended effect of reducing cod
exploitation \citep{Rijnsdorp2001,Dinmore2003}. \\

Even where high-resolution spatiotemporal information is available \citep[see
e.g.][]{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} commercial catch per
unit of effort may still be biased because of fisheries dynamics. Fishers
establish favoured fishing grounds through an explore-exploit strategy
\citep{Rijnsdorp2011, Bailey2018} where they search for areas with high catches
and then use experience to return to areas where they have experienced high
catch in the past. This leads to inherently biased sampling where target
species are over-represented in the catch because fishers exploit areas of high
abundance. For effective adaptive spatial management the effects of
spatiotemporal aggregation in data and fishery targeting need to be understood.
\\

@@

\begin{enumerate}
	\item Do different sources of sampling-derived fisheries data reflect
		the underlying community structure? 	
	\item How do data aggregation and data source impact on the success of
		spatial fisheries management measures?
\end{enumerate}

@@

A Discrete-event simulation (DES) model of a hypothetical fishery was developed
as a software package (\textit{MixFishSim}). The modular approach enabled
efficient computation by allowing for sub-modules implemented on time-scales
appropriate to capture the characteristics of the different processes (Figure
\ref{fig:model}). Sub-modules to capture the full system comprised: 1) population
dynamics, 2) recruitment dynamics, 3) population movement, 4) fishery
dynamics.\\

Population dynamics for any number of species, as chosen by the user, operate
on a daily time-step (with recruitment occurring only during defined seasons
for each population), while population movement occurs on a weekly time-step,
with the fishing module operating on a tow-by-tow basis (i.e., multiple events
a day). \\

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model that models the fish populations in terms
of aggregate biomass of recruits and mature components rather than keeping
track of individuals \citep{Deriso1980, Schnute1985, Dichmont2003}. A daily
time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size. Biomass for each cell $c$ was incremented each day $d$ as
follows (see Table \ref{tab: pop_variable} for all parameter details): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& \left(1 + \rho \right) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& \left(B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + W_{R-1} \cdot \left( \alpha_{d-1} \cdot
	R_{\tilde{y}\left(c\right)}\right) \right)
	\hspace{0.9cm} + \\
	& W_{R} \cdot \left( \alpha_{d} \cdot R_{\tilde{y} \left(c\right)}
	\right) \\
	\end{split}
\end{equation}
where $\rho$ is Ford's growth coefficient shown to be equal to
$\mathrm{e}^{-K}$ when $K$ is the Brody growth coefficient, the rate at which
the asymptote is approached from a von Bertalanffy growth model
\citep{Schnute1985}. $W_{R-1}$ is the average weight of fish prior to
recruitment, while $W_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}(c)}$ is the annual recruits in year $y$ for cell $c$. \\

@@

Recruitment is modelled as a function of adult biomass. In
\textit{MixFishSim}, it can either take the form of a stochastic Beverton-Holt
stock recruitment relationship, or a stochastic Ricker stock recruitment
relationship. The Beverton-Holt relationship is defined as\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha S_{c,d})}{(\beta + S_{c,d})} \\
	     \ln(R_{c,d}) \sim & N[(\ln(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes. The stochastic Ricker form \citep{Ricker1954} is:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
	\ln(R_{c,d}) \sim & N[(\ln(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the
density-dependent reduction in productivity as the SSB increases.

@@

Population movement is a combination of directed (advective) movement where at
certain times of year the population moves towards spawning grounds by
increasing the probabilities of moving into the spawning grounds from adjacent
cells, and random (diffusive) movement, governed by a stochastic process where
movement between adjacent cells is described by a set of probabilities.
Stochastic probabilities are affected by the suitability of habitat,
temperature in a cell and the thermal tolerance of a population to that
temperature.\\

The combined process results in a population structure and movement pattern
unique to each population, with population movement occurring on a weekly
basis. Modelling population movement on a weekly timescale reflects that fish
tend to aggregate in species-specific locations that have been observed to last
between one and two weeks \citep{Poos2007}. Therefore this process approximated
the demographic shifts in fish populations throughout a year with seasonal
spawning patterns (Figure \ref{S-fig:5}). \\

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid. We first defined a Gaussian random field process, $\{S(c) : c
\in \mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the
joint distribution of $S = \{S(c_{1}),\dots S(c_{n})\}$ is multivariate
Gaussian with a \textit{Matérn} covariance structure, where the correlation
strength weakens with distance controlled by two parameters, with $\nu$ a scale
parameter in the units of distance and $\kappa$ a shape parameter which
determines the smoothness of the process. We use the most commonly used Matérn
covariance structure as it is a flexible form that contains the exponential and
double exponential as special cases and it enables us to model the spatial
autocorrelation observed in animal populations where density is more similar in
nearby locations \citep{Tobler1970, F.Dormann2007, Poos2007}. \\
